Automated troubleshooting toolset for SDNs

### 2013-10-27 draft.tex
flowchecker

\subsection{SOFT - \textit{Systematic OpenFlow Testing}}
SOFT is a tool which aims to test the interoperability between OpenFlow switches. On our layering architecure, the OpenFlow protocol appears in the Physical View. SOFT has been designed to identify wrong behaviors of different switches running different implementation of the OpenFlow protocol. Thus, SOFT compare different Physical View of different switches. But SOFT can do more than that. It can also help to find inconsistency in the layers below the Physical Layers. SOFT can be used to check the consistency between the \textit{state layer} of Device State and the \textit{state layer} of Hardware

@@

>>>>

\subsection{SOFT - \textit{Systematic OpenFlow Testing}}

@@

The following tool is particularly adapted for verifying consistency between switches and controller across different OpenFlow federated infrastructures. FlowChecker, based on the ConfigChecker tool, provides a way to detect misconfigurations in the FlowTable of the switches.
